\documentclass[10pt,a4paper]{book}

\usepackage{graphicx}

\begin{document}

\scriptsize

\begin{flushleft}
\textsf{\textbf{  18\, $|$ \,Introduction to Automata Theory, Formal Languages and Computation}}
\end{flushleft}

Let $x \in (rs + rt)$

\begin{center}
  $\qquad\;\Longrightarrow (x \in rs \:or\: x \in rt)$

  $\qquad\qquad\qquad\qquad\qquad\:\;\Longrightarrow (x \in r \:and\: x \in s) or (x \in r \:and\: x \in t)$

  $\qquad\qquad\qquad\Longrightarrow x \in r \:and\: (x \in s \:or\: x \in t)$

  $\Longrightarrow x \in r(s + t)$
\end{center}

That is $(rs + rt) \subseteq r(s + t)$.

\qquad So, $r(s + t) = rs + rt (proved)$.

\begin{flushleft}
3. Prove that
\end{flushleft}

$(A \cup B) \cap (B \cup C) \cap (C \cup A) = (A \cap B) \cup (B \cap C) \cup (C \cap A).$

Solution: From the distributive property, we know $A \cup (B \cap C) = (A \cup B) \cap (B \cup C).$

$$\longrightarrow (B \cup A) \cap (B \cup C) \rightarrow B \cup (A \cap C) \rightarrow B \cup (C \cap A)$$

\textbf{LHS $(A \cup B) \cap (B \cup C) \cap (C \cup A)$}

\begin{center}
  $\Longrightarrow [B \cup (C \cap A)] \cap (C \cup A)$

  $\qquad\qquad\qquad\qquad\qquad\qquad\Longrightarrow [B \cap (C \cup A)] \cup [(C \cap A) \cup(C \cup A)] [As\: A \cap A = A]$

  $\qquad\;\Longrightarrow (B \cap C) \cup(B \cap A) \cup (C \cap A)$

  $\qquad\qquad\qquad\qquad\qquad\Longrightarrow (A \cap B) \cup (B \cap C) \cup (C \cap A) = RHS (proved).$
\end{center}

\begin{flushleft}
  4. Let R be an equivalence relation in $\{0\}^{*}$ with the following equivalence classes:
\end{flushleft}

$[ \:] R = \{0\}^{0}$

$[ 0 ]RR = {0}^{1}$

$[00]R = \{0\}^{2} \cup \{0\}^{3} \cup \{0\}^{4} ……….$

Show that R is right invariant .

\begin{flushleft}
  \qquad\textbf{\textsf{Solution:}} From the defi nition of right invariant, we know that if R is right invariant then for
all x, y, and z,
\end{flushleft}

$$ xRy \Rightarrow xzRyz. $$

From the given equivalence classes,

$\qquad [\: ]_{R} $ means a null string.

$\qquad[0]_{R} $ has only string 0.

$\qquad[00]_{R} $ has strings 00, 000, 0000, ……, etc.

\quad \tiny
\quad

Three cases may occur:

i) \, If x and y are null string, i.e., if x, y $\in [\: ]_{R}$. xz = z and yz = z and zRz holds good.

ii) \,If x, y $\in [0]_{R}, and z \in [ \:]_{_{R}},$ then xz = x and yz = y. So, xRy = xzRyz.

\qquad If z $\in [0]_{R}$, then xz = 00 and yz = 00, Hence, xz = yz, which implies that xzRyz holds good.

\qquad If z $\in [00]_{R}$, then z has at least 2 zeros. This means that xz and yz have at least 3 zeros which

belongs to $[00]_{R}$. This means that xzRyz holds good.

iii) If x, y $\in [00]_{R}$, then x and y each have at least 2 zeros. z may belong to any one of the three,

\qquad but xy and yz produce strings of 2 or more zeros. That is, both of them belong to $[00]_{R}$. This

\qquad means that xzRyz holds good.

\end{document}
